---
title: "EZBHDDM: Within-subject simulation study on hypothesis testing"
author: "Adriana F. Chávez De la Peña"
date: "`r Sys.Date()`"
output:
  rmdformats::material:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: true
    cards: false
    highlight: tango
    fig_width: 12 
    fig_height: 8 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(rmdformats)
library(here)
# Explicitly tell here where this file is located relative to project root
here::i_am("demos/simulation-studies/hypothesis_testing/report/simulationReport_HT.Rmd")
```


```{r, echo=FALSE}
library(here)

for(archive in dir(here("src"))){    
    if(archive == "README.md") next
    source(paste(here("src/"),archive,sep=""))     }
for(archive in dir(here("demos", "simulation-studies", "hypothesis_testing", "src"))){ 
     source(paste(here("demos", "simulation-studies", "hypothesis_testing", "src", archive),sep=""))     }
```

# Introduction

In this simulation study, paired choice and response time observations are generated from the three-parameter DDM with different parameter values for each participant, and a within-participant t-test design on the drift rate:

\begin{align*}
\mathbf{Y}_{i,k} &\sim \mbox{DDM}\bigl(\nu_{i,k}, \alpha_{i}, \tau_{i} \bigl)\\
i &\in \{1, ..., P\}\\
k &\in \{1, 2\}\\
\end{align*}

So for every participant $i$, two conditions $k$ are generated, with different drift rates $\nu_{i,k}$, boundary separation $\alpha_{i}$, and non-decision time $\tau_{i}$.

Upon generating the data, we compute the EZ-DDM summary statistics (i.e., the mean accuracy rate and the mean and variance of the response times observed) to fit a Bayesian Hierarchical EZ-DDM with the following higher-level structure:

\begin{align*}
\nu_{i,k} &\sim \mbox{Normal}\left(\mu_\nu+\beta_{k}\mbox{X}_{k}, \sigma_\nu\right)\\
\alpha_{i} &\sim \mbox{Normal}\left(\mu_\alpha, \sigma_\alpha\right)\\
\tau_{i} &\sim \mbox{Normal}\left(\mu_\tau, \sigma_\tau\right)\\
\end{align*}

# Simulation-study results

Results from this simulation study are stored in the directory `output/RData-results/`.

## Rhat check

We first check the Rhat convergence diagnostic for all the chains.

```{r}
check_BetaSimulationRhats(here("output/RData-results/simHypTesting_P40T80_B.RData"))
```

```{r}
check_BetaSimulationRhats(here("output/RData-results/simHypTesting_P40T80_B1.RData")) 
```

```{r}
check_BetaSimulationRhats(here("output/RData-results/simHypTesting_P40T80_B2.RData")) 
```




```{r, eval=FALSE}
setwd("../../../../../../Dropbox/achavezd/samples/tmp2/")

betaNoDiff <- HDDM_simFixedEffect(nParticipants = 40, nTrialsPerCondition = 160, nDatasets = 1000, beta.effect = 0, 
                         priors = NA, n.chains = 4, Show = TRUE, forceSim = FALSE, fromPrior = FALSE, label= "Null")

betaDiff1 <- HDDM_simFixedEffect(nParticipants = 40, nTrialsPerCondition = 160, nDatasets = 1000, beta.effect = 0.1, 
                         priors = NA, n.chains = 4, Show = TRUE, forceSim = FALSE, fromPrior = FALSE, label="Diff1")

betaDiff2 <- HDDM_simFixedEffect(nParticipants = 40, nTrialsPerCondition = 160, nDatasets = 1000, beta.effect = 0.2, 
                         priors = NA, n.chains = 4, Show = TRUE, forceSim = FALSE, fromPrior = FALSE, label="Diff2")

betaDiff3 <- HDDM_simFixedEffect(nParticipants = 40, nTrialsPerCondition = 160, nDatasets = 1000, beta.effect = 0.3, 
                         priors = NA, n.chains = 4, Show = TRUE, forceSim = FALSE, fromPrior = FALSE, label="Diff3")

betaDiff4 <- HDDM_simFixedEffect(nParticipants = 40, nTrialsPerCondition = 160, nDatasets = 1000, beta.effect = 0.4, 
                         priors = NA, n.chains = 4, Show = TRUE, forceSim = FALSE, fromPrior = FALSE, label="Diff4")

betaDiff5 <- HDDM_simFixedEffect(nParticipants = 40, nTrialsPerCondition = 160, nDatasets = 1000, beta.effect = 0.5, 
                         priors = NA, n.chains = 4, Show = TRUE, forceSim = FALSE, fromPrior = FALSE, label="Diff5")


```

```{r, eval=FALSE}
par(pty="m",mai=c(0.7,0.25,0,0), oma= c(0,0,1,1.5))

plot_post_b0 <- function(betaNoDiff, betaDiff){
        beta.0 <- betaNoDiff$estimates[,"betaweight"]
        beta.1 <- betaDiff$estimates[,"betaweight"]
        mpb0 <- mean(beta.0)
        mpb1 <- mean(beta.1)
        ci.b0 <- quantile(beta.0,probs = c(0.025,0.975))
        ci.b1 <- quantile(beta.1,probs = c(0.025,0.975))
        ci.b0.x <- density(beta.0)$x[which(density(beta.0)$x>ci.b0[1]&density(beta.0)$x<ci.b0[2])]
        ci.b0.y <- density(beta.0)$y[which(density(beta.0)$x>ci.b0[1]&density(beta.0)$x<ci.b0[2])]
        ci.b1.x <- density(beta.1)$x[which(density(beta.1)$x>ci.b1[1]&density(beta.1)$x<ci.b1[2])]
        ci.b1.y <- density(beta.1)$y[which(density(beta.1)$x>ci.b1[1]&density(beta.1)$x<ci.b1[2])]
        curve0 <-"#AEBBD0"
        line0 <- "#4B8CF4"
        curve1 <-"#E4C99A"
        line1 <- "#C47F07"
        maxY <- max(density(beta.0)$y,density(beta.1)$y)*1.15
        ci0 <- rgb(162/255,175/255,255/255,0.4)
        ci1 <- rgb(250/255,128/255,105/255,0.4)
        hist(beta.0, freq = FALSE, breaks = 40, col=curve0, border = "black", ylim = c(0,maxY),
             ann=F, axes = F, xlim=c(-0.2,0.7))
        hist(beta.1, freq = FALSE, breaks = 40, col=curve1, border = "black", add=TRUE, ylim = c(0,maxY))
        axis(1,seq(-0.2,0.7,0.05),seq(-0.2,0.7,0.05))
        lines(density(beta.0), lwd=4, col="black")
        lines(density(beta.1), lwd=4, col="black")
        polygon(x=c(ci.b0.x,rev(ci.b0.x)),c(rep(0,length(ci.b0.y)),rev(ci.b0.y)), col=ci0, border=line0,lwd=3)
        polygon(x=c(ci.b1.x,rev(ci.b1.x)),c(rep(0,length(ci.b1.y)),rev(ci.b1.y)), col=ci1, border=line1,lwd=3)
        abline(v=c(0,0.5), lwd=3, lty=3)
        points(mpb0,0,pch=15,col="#1637DC", cex=1.5)
        points(mpb1,0,pch=15,col="#FF5700", cex=1.5)
        legend(0.48,7.7, expression(paste("True ", beta, " = ", 0.5)), cex=1.3, col="black", adj=0.1, bty="n")
        legend(-0.24,7.7, expression(paste("True ", beta, " = ", 0)), cex=1.3, col="black", adj=0.1, bty="n")
        legend(-0.1,1.2, paste("Average = ",round(mpb0,4)), cex=0.7, bg="#ABB3D8", adj=0.1, box.col = "#1637DC")
        legend(0.4,1.2, paste("Average = ",round(mpb1,4)), cex=0.7, bg="#E2A384", adj=0.1, box.col = "#FF5700")
        text(0.17,6, paste("95% mean posteriors"), cex=0.9, f=2, col=line0)
        text(0.17,5.5, paste("[", round(ci.b0[1],2),",",round(ci.b0[2],2),"]"), cex=0.8, col=line0, f=2)
        text(0.3,4.8, paste("95% mean posteriors"), cex=0.9, f=2, col=line1)
        text(0.3,4.3, paste("[", round(ci.b1[1],2),",",round(ci.b1[2],2),"]"), cex=0.8, col=line1, f=2)
        mtext(expression(paste("Mean posterior ", beta)),1,line=2.5, cex=1.1)
}

plot_post_b0(betaNoDiff, betaDiff)
```


```{r, echo=FALSE, eval=FALSE}
png(file = "../../figures/hypoTest_meanPosts.png", width = 6, height = 3.5, units="in",res=300)
par(pty="m", mai=c(0.7,0.25,0,0), oma= c(0,0,1,1.5), bg=NA)
plot_post_b0(betaNoDiff, betaDiff)
dev.off()
```