---
title: "EZ Bayesian Hierarchical Drift Diffusion Model"
author: "Adriana F. Chavez"
subtitle: "Based on Joachim's python code"
date: "Last time knitted: `r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=1cm,right=1cm,top=2cm,bottom=2cm"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

-------------------

# Basic functions to generate DDM data

```{r}
# Part 1: Simulate single trial outcome
simulate_ddm <- function(a, v, dt, max_steps){
     x <- 0   
     random_dev <- rnorm(max_steps)  
     # Scale step changes by dt
     noise <- random_dev * sqrt(dt)
     drift <- v * dt
     
     for(i in 2:max_steps){
        this_step = drift + noise[i]
        x = x + this_step
            if(abs(x)>=(a/2)){  break  }
     }
     output <- list("RT" = (i+1)*dt, "C"  = x)
     return(output)
}

# Part 2: Simulate over 'n' trials
wdmrnd <- function(a,v,t,n){
    dt = 0.001
    max_steps = 10 / dt
    rt = rep(NA,n)
    accuracy = rep(NA,n)
    
    for(i in 1:n){
        X <- simulate_ddm(a, v, dt, max_steps)
        rt[i] <- X$RT 
        if(X$C>0){  accuracy[i] <- 1
          }else{    accuracy[i] <- 0  }
    }
    output <- data.frame("RT" = rt + t, "accuracy" = accuracy)
    return(output)
}
```

# Example: Generate some data

```{r}
a = 1.50
v = 0.00
t = 0.30
n = 10000

data <- wdmrnd(a, v, t, n)
rt <- data$RT
accuracy <- data$accuracy
```

```{r, echo=FALSE, fig.height=3.5}
par(mfrow = c(1, 3), 
    mar =c(5.1,2,4.1,2),
    bty = "o")

hist(rt[accuracy==1], ann=F, axes=F, breaks=50, col="lightgreen",
     border=NA)
mtext("Distribution of Reaction Times", 3, cex=0.65, line=0.5)
mtext("Reaction Time", 1, cex=0.6, line=2)
mtext("Count", 2, cex=0.6, line=1)
legend("topright", col="lightgreen", "Correct", pch=15, cex=0.7, bty="n")
axis(1,c(0:5),line=-0.7)

hist(rt[accuracy==0], ann=F, axes=F, breaks=50, col="indianred1",
     border=NA)
mtext("Distribution of Reaction Times", 3, cex=0.65, line=0.5)
mtext("Reaction Time", 1, cex=0.6, line=2)
mtext("Count", 2, cex=0.6, line=1)
legend("topright", col="indianred1", "Incorrect", pch=15, cex=0.7, bty="n")
axis(1,c(0:5),line=-0.7)

barplot(c(sum(1-accuracy),sum(accuracy)), ann=F, axes=F,
        col=c("red3","springgreen3"))
mtext("Accuracy Histogram", 3, cex=0.65, line=0.5)
mtext("Count", 2, cex=0.6, line=1)
axis(1,c(0.7,1.9),c("Incorrect","Correct"))
```


\clearpage

# Simulation Study environment and variables

### Auxiliary functions

The code for the auxiliary functions is hidden from this .pdf file (but can be checked on the .Rmd file). The auxiliary functions are:

1. `design_summary`: A function to print the settings used in the simulation
2. `default_priors`: A function to load and print default prior values
3. `write_JAGSmodel`: A function to write the JAGS model using the prior values
4. `data_toJAGS`: A function to create a list with all the data objects in the JAGS model
5. `default_inits`:  
6. `extractSamples`: A function to extract individual samples for any parameter

```{r, echo=FALSE}
################################################################
####    Auxiliary functions   ##################################
################################################################

# A function to print the settings used in the simulation
design_summary = function(settings){
          cat("========== EZBHDDM Design Parameters: =======\n")
          cat("Number of Participants:    ", settings$nPart,"\n")
          cat("Trials Per Person:",settings$nTrials,"\n")
          cat("Priors:\n")
          t(settings$prior)
}

# A function to load and print default prior values
default_priors <- function(Show=TRUE){
    prior <- data.frame("bound_mean_mean" = 1.50,
                        "bound_mean_sdev" = 0.20,
                        "drift_mean_mean" = 0.00,
                        "drift_mean_sdev" = 0.50,
                        "nondt_mean_mean" = 0.30,
                        "nondt_mean_sdev" = 0.06,
                        "bound_sdev_lower" = 0.10,
                        "bound_sdev_upper" = 0.20,
                        "drift_sdev_lower" = 0.20,
                        "drift_sdev_upper" = 0.40,
                        "nondt_sdev_lower" = 0.01,
                        "nondt_sdev_upper" = 0.05)
    if(Show){
          cat("========== EZBHDDM Priors: ===============\n")
          cat("Bound Mean Mean:   ", prior$bound_mean_mean,"\n")
          cat("Bound Mean Std Dev:",prior$bound_mean_sdev,"\n")
          cat("Drift Mean Mean:   ",prior$drift_mean_mean,"\n")
          cat("Drift Mean Std Dev:",prior$drift_mean_sdev,"\n")
          cat("Non-decision Time Mean Mean:",prior$nondt_mean_mean,"\n")
          cat("Non-decision Time Mean Std: ", prior$nondt_mean_sdev,"\n")
          cat("Bound Std Dev Shape:",prior$bound_sdev_lower,"\n")
          cat("Bound Std Dev Scale:",prior$bound_sdev_upper,"\n")
          cat("Drift Std Dev Shape:",prior$drift_sdev_lower,"\n")
          cat("Drift Std Dev Scale:",prior$drift_sdev_upper,"\n")
          cat("Non-decision Time Shape:",prior$nondt_sdev_lower,"\n")
          cat("Non-decision Time Scale:",prior$nondt_sdev_upper,"\n")
    }
  return(prior)
}

# A function to write the JAGS model using the prior values
write_JAGSmodel <- function(prior,modelFile = "EZHBDDM.bug"){
      modelFile <- "EZHBDDM.bug"
      
      opening <- "model{"
      prior.bound_m <- paste("          bound_mean ~ dnorm(", prior$bound_mean_mean,",pow(",prior$bound_mean_sdev,",-2))T(0.10,3.00)", sep="")
      prior.drift_m <- paste("          drift_mean ~ dnorm(", prior$drift_mean_mean,",pow(",prior$drift_mean_sdev,",-2))T(-3.00,3.00)", sep="")
      prior.nondt_m <- paste("          nondt_mean ~ dnorm(", prior$nondt_mean_mean,",pow(",prior$nondt_mean_sdev,",-2))T(0.05,1.00)", sep="")
      prior.bound_sd <- paste("          bound_sdev ~ dunif(", prior$bound_sdev_lower,",",prior$bound_sdev_upper,")", sep="")
      prior.drift_sd <- paste("          drift_sdev ~ dunif(", prior$drift_sdev_lower,",",prior$drift_sdev_upper,")", sep="")
      prior.nondt_sd <- paste("          nondt_sdev ~ dunif(", prior$nondt_sdev_lower,",",prior$nondt_sdev_upper,")", sep="")
      content <-"
              # Sampling model
              for (p in 1:nParticipants){
                  bound[p] ~ dnorm(bound_mean, pow(bound_sdev, -2))T(0.10,3.00)
                  drift[p] ~ dnorm(drift_mean, pow(drift_sdev, -2))T(-3.00,3.00)
                  nondt[p] ~ dnorm(nondt_mean, pow(nondt_sdev, -2))T(0.05,1.00)
                  
                  # Forward equations from EZ Diffusion
                  ey[p]  = exp(-bound[p] * drift[p])
                  Pc[p]  = 1 / (1 + ey[p])
                  PRT[p] = 2 * pow(drift[p], 3) / bound[p] * pow(ey[p] + 1, 2) / (2 * -bound[p] * drift[p] * ey[p] - ey[p]*ey[p] + 1)
                  MDT[p] = (bound[p] / (2 * drift[p])) * (1 - ey[p]) / (1 + ey[p])
                  MRT[p] = MDT[p] + nondt[p]
              
                  # Loss functions using MRT, PRT, and Pc
                  meanRT[p]  ~ dnorm(MRT[p], PRT[p] * correct[p])
                  varRT[p]   ~ dnorm(1/PRT[p], 0.5 * correct[p] * PRT[p] * PRT[p])
                  correct[p] ~ dbin(Pc[p], nTrialsPerPerson)
              }
      }"
      
      final_file <- file(modelFile)
            writeLines(c(opening,prior.bound_m,prior.drift_m,prior.nondt_m,
                         prior.bound_sd,prior.drift_sd,prior.nondt_sd,content),
                       final_file)
      close(final_file)
}

# A function to create a list with all the data objects in the JAGS model
data_toJAGS <- function(){
    passData <- list("nParticipants", "nTrialsPerPerson",
                     "meanRT", "varRT", "correct")
    return(passData)
}

default_inits <- function(n.chains,nParticipants){
  myinits <- rep(list(list()), n.chains)
  for(i in 1:n.chains){
      myinits[[i]] <- list(drift = rnorm(nParticipants,0,0.1))
  }
  return(myinits)
}

# A function to extract individual samples for any parameter
extractSamples <- function(parameter.name, samples){
        postParam.Array <- samples$BUGSoutput$sims.array
        samplesID <- names(postParam.Array[1,1,])
        locateParameter  <- which(grepl(parameter.name,samplesID))
        
        param.is.hierarchical <- length(which(grepl("_",parameter.name)))!=0
        if(!param.is.hierarchical){
          locateHierPar <- which(grepl("_",samplesID))
          locateParameter <- locateParameter[!locateParameter %in% locateHierPar]   
        }
        
        # Now, for individual/task level parameters...
        if(length(locateParameter)>1){
              # We isolate the pages ID that contain the parameter of interest
              samplesRelated <- samplesID[locateParameter]
              # We identify the maximum index
              locateParticipantID <-as.numeric(gsub("\\D", "", samplesRelated))
              nP <- max(locateParticipantID,na.rm = TRUE)
              # We locate the page ID containing the last index
              lastP <- which(grepl(nP,samplesRelated))
              # And isolate all IDs from there
              locateParameter <- samplesRelated[(lastP-nP)+1:lastP]
        }
        # We retrieve only the pages containing the parameter
        x <- postParam.Array[,,locateParameter]
return(x)
}

plot.Chain <- function(samples){
  posterior.samples <- samples$BUGSoutput$sims.array
  labels <- names(posterior.samples[1,1,])
  N <- dim(posterior.samples)[3]
  factors <- which((N %% 1:N) == 0)
  

  
  par(mfrow = c(1, 3), 
      mar =c(5.1,2,4.1,2),
      bty = "o")
  for(i in 1:N){
      plot(posterior.samples[,1,i], type="l", main=labels[i], xlab="Iteration",
           ylab="Value sampled")  
      if(n.chains>1){
           for(a in 2:n.chains){
           lines(posterior.samples[,a,i],col=a)
           }
        }
  }
}
```

### Core functions

```{r, echo=FALSE, message=FALSE, results='hide'}
nSim <- 200
prior <- default_priors()
nParticipants <- 50
nTrials <- 150
n.chains = 4
save_sampleFiles = FALSE
samplesFileName = "samples.RData"
settings <- list("nPart"   = nParticipants,
                 "nTrials" = nTrials,
                 "prior"   = prior)
```

```{r}
################################################################
####    Core functions       ##################################
################################################################

# Sample 'true' parameter values from the priors specified
sample_parameters <- function(settings){
    prior <- settings$prior
    nP <- settings$nPart
    bound_mean <- rnorm(1,prior$bound_mean_mean,prior$bound_mean_sdev)
    drift_mean <- rnorm(1,prior$drift_mean_mean,prior$drift_mean_sdev)
    nondt_mean <- rnorm(1,prior$nondt_mean_mean,prior$nondt_mean_sdev)
    bound_sdev <- runif(1,prior$bound_sdev_lower,prior$bound_sdev_upper)
    drift_sdev <- runif(1,prior$drift_sdev_lower,prior$drift_sdev_upper)
    nondt_sdev <- runif(1,prior$nondt_sdev_lower,prior$nondt_sdev_upper)
    bound <- rnorm(nP,bound_mean, bound_sdev)
    drift <- rnorm(nP,drift_mean, drift_sdev)
    nondt <- rnorm(nP,nondt_mean, nondt_sdev)
    parameter_set <- list("bound_mean" = bound_mean, "drift_mean" = drift_mean,
                          "nondt_mean" = nondt_mean, "bound_sdev" = bound_sdev,
                          "drift_sdev" = drift_sdev, "nondt_sdev" = nondt_sdev,
                          "bound" = bound,   "drift" = drift,   "nondt" = nondt)
  return(parameter_set)
}

# Sample data using simulation settings and parameter values sampled
sample_data <- function(settings, parameter_set){
  nObs = settings$nPart*settings$nTrials
  data = matrix(NA,ncol=3,nrow=nObs)
  data[,1] = rep(1:settings$nPart, each=settings$nTrials)
  for(i in 1:settings$nP){
      this.sub <- which(data[,1]==i)
      accuracy = 0
      while(sum(accuracy)==0){
            temp <- wdmrnd(a = parameter_set$bound[i], 
                           v = parameter_set$drift[i], 
                           t = parameter_set$nondt[i], 
                           n = settings$nTrials)
            accuracy = temp$accuracy
      }
      data[this.sub,3] = accuracy
      data[this.sub,2] = temp$RT
  }
  data = as.data.frame(data)
  colnames(data) <- c("sub", "rt", "accuracy")
  return(data)
}

# Get individual statistics from full data: mean acc and correct-rt mean and var
get_Statistics <- function(data){
  if(is.null(data$accuracy)|is.null(data$rt)){
        error.msg = "Data not available."
        return(print(error.msg))
  }
  subID  = unique(data$sub)
  sum_correct = tapply(data$accuracy, data$sub, sum)  
  always_0 = which(sum_correct==0)
  if(length(always_0)!=0){
    bad_participants = (data$sub %in% always_0)
    data = data[-bad_participants,]
    sum_correct     = tapply(data$accuracy, data$sub, sum) 
  }
  mean_accuracy   = tapply(data$accuracy, data$sub, mean) 
  
  keep.correct = which(data$accuracy==1)
  correct_only = data[keep.correct,]
  mean_rt_correct = tapply(correct_only$rt, correct_only$sub, mean)
  var_rt_correct  = tapply(correct_only$rt, correct_only$sub, var)
  
  data_statistics = cbind(subID, sum_correct, mean_accuracy, mean_rt_correct, var_rt_correct)
  data_statistics = as.data.frame(data_statistics)
  colnames(data_statistics) = c("sub", "sum_correct","meanAccuracy", "meanRT_correct", "varRT_correct")
  return(data_statistics)
}

# Run JAGS and extract mean posteriors for all relevant parameters
getJAGS_estimates <- function(modelFile="./EZHBDDM.bug", samplesFile=NA){
    parameters <- c("bound_mean", "drift_mean", "nondt_mean", "bound", "nondt",
                    "drift_sdev", "nondt_sdev", "bound_sdev", "drift")
    library(R2jags)  
    samples <- jags(data=data, 
                    parameters.to.save=parameters, 
                    model=modelFile, 
                    n.chains=n.chains, 
                    n.iter=1000, 
                    n.burnin=200, 
                    n.thin=1, 
                    DIC=T, 
                    inits=myinits)
    if(!is.na(samplesFile)){
       save(samples,file=samplesFile)
    }
    
    # Isolate samples related to the drift parameter
    samples.drift = extractSamples("drift", samples)
    samples.drift_mean = extractSamples("drift_mean", samples)
    samples.drift_sdev = extractSamples("drift_sdev", samples)
    # Isolate samples related to the bound parameter
    samples.bound = extractSamples("bound", samples)
    samples.bound_mean = extractSamples("bound_mean", samples)
    samples.bound_sdev = extractSamples("bound_sdev", samples)
    # Isolate samples related to the nondt parameter
    samples.nondt = extractSamples("nondt", samples)
    samples.nondt_mean = extractSamples("nondt_mean", samples)
    samples.nondt_sdev = extractSamples("nondt_sdev", samples)
    estimates <- list("drift" = apply(samples.drift,3,mean),
                      "nondt" = apply(samples.nondt,3,mean),
                      "bound" = apply(samples.bound,3,mean),
                      "drift_mean" = mean(samples.drift_mean),
                      "drift_sdev" = mean(samples.drift_sdev),
                      "bound_mean" = mean(samples.bound_mean),
                      "bound_sdev" = mean(samples.bound_sdev),
                      "nondt_mean" = mean(samples.nondt_mean),
                      "nondt_sdev" = mean(samples.nondt_sdev))
return(estimates)
}
```

### Main functions

```{r, eval=FALSE}
Hddm_Data <- function(settings, parameter_set){
    rawData = sample_data(settings,parameter_set)
    sumData = get_Statistics(rawData)
    jagsData = data_toJAGS()
    return(list("rawData" = rawData, 
                "sumData" = sumData,
                "jagsData" = jagsData))
}

Hddm_Design = function(nParticipants, nTrials, prior, 
                       n.chains = 4, samplesFile = NA){
    
    settings <- list("nPart"   = nParticipants,
                     "nTrials" = nTrials,
                     "prior"   = prior)
    parameter_set = sample_parameters(settings)
    
    getData <- Hddm_Data(settings,parameter_set)
    sub     <- getData$sumData$sub
    correct <- getData$sumData$sum_correct
    varRT   <- getData$sumData$varRT_correct
    meanRT  <- getData$sumData$meanRT_correct
    nTrialsPerPerson <- as.numeric(unique(tapply(getData$rawData$accuracy,getData$rawData$sub,length)))
    nParticipants    <- length(getData$sumData$sub)
    
    write_JAGSmodel(prior)
    data <- getData$jagsData
    myinits <- default_inits(n.chains, settings$nPart)
    
    estimates <- getJAGS_estimates()
  
    output <- list("trueValues" = parameter_set,
                   "estValues" = estimates)
return(output)
}

```



```{r, eval=FALSE}
class Hddm_Parameter_Set:
    def __init__(self,
                 bound_mean = None, bound_sdev = None, bound = None,
                 drift_mean = None, drift_sdev = None, drift = None,
                 nondt_mean = None, nondt_sdev = None, nondt = None):
        self.bound_mean = bound_mean
        self.bound_sdev = bound_sdev
        self.bound      = bound
        self.drift_mean = drift_mean
        self.drift_sdev = drift_sdev
        self.drift      = drift
        self.nondt_mean = nondt_mean
        self.nondt_sdev = nondt_sdev
        self.nondt      = nondt

    def __sub__(self, other):
        if not isinstance(other, Hddm_Parameter_Set):
            return None

        return Hddm_Parameter_Set(
            bound_mean = self.bound_mean - other.bound_mean,
            bound_sdev = self.bound_sdev - other.bound_sdev,
            drift_mean = self.drift_mean - other.drift_mean,
            drift_sdev = self.drift_sdev - other.drift_sdev,
            nondt_mean = self.nondt_mean - other.nondt_mean,
            nondt_sdev = self.nondt_sdev - other.nondt_sdev,
            bound      = self.bound - other.bound if self.bound is not None and other.bound is not None else None,
            drift      = self.drift - other.drift if self.drift is not None and other.drift is not None else None,
            nondt      = self.nondt - other.nondt if self.nondt is not None and other.nondt is not None else None
        )

    def __str__(self):
        output = [
            "Hddm_Parameter_Set Details:",
            f"Bound Mean:              {self.bound_mean}",
            f"Bound Std Dev:           {self.bound_sdev}",
            f"Drift Mean:              {self.drift_mean}",
            f"Drift Std Dev:           {self.drift_sdev}",
            f"Non-decision Time Mean:  {self.nondt_mean}",
            f"Non-decision Time Std:   {self.nondt_sdev}",
            f"Bound:                   {self.bound}",
            f"Drift:                   {self.drift}",
            f"Non-decision Time:       {self.nondt}"
        ]
        return '\n'.join(output)

```

```{r}

```

```{r, eval=FALSE}
Hddm_Design = function(nParticipants, nTrials, prior){
  

    

    def estimate_parameters(self):
        # This is the key bit
        code = f"""
        JAGS
        """

        data, valid_indices = self.data.to_jags()

        n_Participants_Left = data['nParticipants']

        # Initial values
        init = { "drift" : np.random.normal(0, 0.1, n_Participants_Left) }

        try:
            model = pyjags.Model(
                progress_bar = False,
                code    = code,
                data    = data,
                init    = init,
                adapt   = 100,
                chains  = 4,
                threads = 4)
        except Exception as e:
            #error_message = str(e)
            #print(type(error_message))
            #print(error_message)
            #self.data.summary()
            #print(self.data.to_jags())
            #print(self.parameter_set)
            print('e', end='')
            return
        
        samples = model.sample(400, 
                               vars = ['bound_mean', 'drift_mean', 'nondt_mean',
                                       'bound_sdev', 'drift_sdev', 'nondt_sdev',
                                       'bound',      'drift',      'nondt'])

        # Annoying management of sample object...  First move individual parameters to their own fields
        for i in np.arange(0, n_Participants_Left):
            samples.update({'bound_'+str(valid_indices[i]): samples['bound'][i,:,:], 
                            'drift_'+str(valid_indices[i]): samples['drift'][i,:,:], 
                            'nondt_'+str(valid_indices[i]): samples['nondt'][i,:,:], })

        # ... remove the old unwieldy matrices 
        for s in ["bound", "drift", "nondt"]:
            samples.pop(s)

        # Start a new dict with estimates only
        estimate = { "bound": [np.nan] * self.n_Participants,
                     "drift": [np.nan] * self.n_Participants,
                     "nondt": [np.nan] * self.n_Participants
                   }
        
        for varname in ['bound_mean', 'drift_mean', 'nondt_mean',
                        'bound_sdev', 'drift_sdev', 'nondt_sdev']:
            estimate.update({varname: np.mean(samples[varname])})

        # ... make new, wieldy matrices
        for i in valid_indices:
            estimate['bound'][i] = np.mean(samples['bound_'+str(i)])
            estimate['drift'][i] = np.mean(samples['drift_'+str(i)])
            estimate['nondt'][i] = np.mean(samples['nondt_'+str(i)])

        # Copy estimate to design object
        self.estimate = Hddm_Parameter_Set()
        self.estimate.bound_mean = estimate['bound_mean']
        self.estimate.drift_mean = estimate['drift_mean']
        self.estimate.nondt_mean = estimate['nondt_mean']
        self.estimate.bound_sdev = estimate['bound_sdev']
        self.estimate.drift_sdev = estimate['drift_sdev']
        self.estimate.nondt_sdev = estimate['nondt_sdev']
        self.estimate.bound      = estimate['bound']
        self.estimate.drift      = estimate['drift']
        self.estimate.nondt      = estimate['nondt']
        
```







# Run simulations

### Simple example 

```{r, eval=FALSE}
set.seed(123)

prior <- default_priors()

write_JAGSmodel(prior)

design <- Hddm_Design(nParticipants = 20, nTrials = 50, prior = prior)

design.sample_parameters()
design.sample_data()
design.estimate_parameters()
```

### Simulation study (200 repetitions)

```{r, eval=FALSE}
nSim <- 200
prior <- default_priors()
settings <- list("nPart"   = 50,
                 "nTrials" = 150,
                 "prior"   = prior)


tru = [Hddm_Parameter_Set()] * K
est = [Hddm_Parameter_Set()] * K
err = [Hddm_Parameter_Set()] * K

for(k in 1:nSim){
    set.seed(k)
    cat("Iteration", k+1, "of", nSim)
    design = Hddm_Design(participants=20, trials=50, prior=prior)
    design.sample_parameters()
    design.sample_data()
    #print(design.parameter_set)
    #design.data.summary()
    design.estimate_parameters()
    tru[k] = design.parameter_set
    est[k] = design.estimate
    if design.estimate is not None:
        err[k] = (design.estimate - design.parameter_set)
    else:
        err[k] = None
    if (k+1) % 100 == 0:
        print(f'. {k+1} of {K}\n', end='')
    else:
        print('.', end='')
}
```

```{r, eval=FALSE}
def recovery_plot(x, y, parameterName, ttl):
    fontsize = 10
    
    plt.figure(figsize=(2, 2))
    
    plt.scatter(x, y, color='b', s=3)
    plt.grid()
    plt.gca().set_aspect('equal')
    
    xax = np.linspace(min(x), max(x), 100)
    
    plt.plot(xax, xax, '--')
    
    plt.xlabel('Simulated value', fontsize=10)
    plt.title('Group mean ' + parameterName, fontsize=10)
    
    output_path = "ezrecovery_" + parameterName + ".pdf" 
    plt.savefig(output_path, format='pdf', bbox_inches='tight')
    
    plt.show()
```

```{r, eval=FALSE}
x = [np.nan] * K
y = [np.nan] * K
for k in range(K):
    if err[k] is not None:
       x[k] = tru[k].nondt_mean
       y[k] = est[k].nondt_mean
        
recovery_plot(x, y, 'nondt', 'Group mean nondt')

x = [np.nan] * K
y = [np.nan] * K
for k in range(K):
    if err[k] is not None:
       x[k] = tru[k].drift_mean
       y[k] = est[k].drift_mean

recovery_plot(x, y, 'drift', 'Group mean drift')

x = [np.nan] * K
y = [np.nan] * K
for k in range(K):
    if err[k] is not None:
       x[k] = tru[k].bound_mean
       y[k] = est[k].bound_mean

recovery_plot(x, y, 'bound', 'Group mean bound')

x = np.empty(0)
y = np.empty(0)
for k in range(K):
    if err[k] is not None:
       x = np.append(x, tru[k].drift)
       y = np.append(y, est[k].drift)

recovery_plot(x, y, 'drift', 'Individual drift rates')
```


```{r, echo=FALSE, eval=FALSE}
def __str__(self):
        output = [
            "Hddm_Data Details:",
            f"Person:    {self.person}",
            f"RT:        {self.rt}",
            f"Accuracy:  {self.accuracy}"
        ]
        return '\n'.join(output)
```