---
title: "EZ Bayesian Hierarchical Drift Diffusion Model"
author: "Adriana F. Chavez De la Pena"
date: "Last time knitted: `r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=1cm,right=1cm,top=2cm,bottom=2cm"
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[L]{EZ Bayesian Hierarchical Drift Diffusion Model}
- \fancyfoot[LE,RO]{\thepage}
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(rstan)
```

-------------------

# Basic functions to generate DDM data

\begin{align*}
\mathbf{Y} \sim \mbox{DDM}\bigl(\alpha, \nu, \tau \bigl)
\end{align*}

```{r generate-DDM-data, file='./code/functions/generate_data.R'}
```

# Example: Generate some data

```{r example-parameters}
a = 1.50
v = 0.00
t = 0.30
n = 10000

data <- wdmrnd(a, v, t, n)
```

```{r example-plot, echo=FALSE, fig.height=3.5, file="./code/scripts/plot_data.R"}
par(mfrow = c(1, 3), 
    mar =c(5.1,2,4.1,2),
    bty = "o")

rt <- data$RT
accuracy <- data$accuracy

hist(rt[accuracy==1], ann=F, axes=F, breaks=50, col="lightgreen",
     border=NA)
mtext("Distribution of Reaction Times", 3, cex=0.65, line=0.5)
mtext("Reaction Time", 1, cex=0.6, line=2)
mtext("Count", 2, cex=0.6, line=1)
legend("topright", col="lightgreen", "Correct", pch=15, cex=0.7, bty="n")
axis(1,c(0:5),line=-0.7)

hist(rt[accuracy==0], ann=F, axes=F, breaks=50, col="indianred1",
     border=NA)
mtext("Distribution of Reaction Times", 3, cex=0.65, line=0.5)
mtext("Reaction Time", 1, cex=0.6, line=2)
mtext("Count", 2, cex=0.6, line=1)
legend("topright", col="indianred1", "Incorrect", pch=15, cex=0.7, bty="n")
axis(1,c(0:5),line=-0.7)

barplot(c(sum(1-accuracy),sum(accuracy)), ann=F, axes=F,
        col=c("red3","springgreen3"))
mtext("Accuracy Histogram", 3, cex=0.65, line=0.5)
mtext("Count", 2, cex=0.6, line=1)
axis(1,c(0.7,1.9),c("Incorrect","Correct"))
```

\clearpage

# Simulation Study functions and variables

The code for the functions listed below is hidden from this pdf file (but can be checked on the .Rmd). Here we present a list of what these functions are and what they do!

## Auxiliary functions

1. `nameOutput` : A function to generate an appropriate output name based on the number of trials and participants.
2. `design_summary`: A function to print the settings used in the simulation.
3. `show_priors`: A function to print the default prior values.
4. `show_parameters`: A function to print the parameter values used to generate data used in the simulation.

```{r, echo=FALSE}
# A function to generate an appropriate outputFile name based on the number of trials and participants
nameOutput <- function(nTrials, nParticipants){
  fileName <- paste("./sim_P",nParticipants,"T",nTrials,".RData", sep="")
  return(fileName)
}

# A function to print the settings used in the simulation
design_summary = function(nParticipants, nTrials, nConditions=NA){
    cat("========== EZBHDDM Design Parameters: =======\n")
    cat("Number of Participants:    ", nParticipants,"\n")
    if(is.na(nConditions)){
       cat("Trials Per Person:         ",nTrials,"\n")
    }else{
       cat("Number of Conditions:      ", nParticipants,"\n")  
       cat("Trials Per Conditin:       ",nTrials,"\n")
    }
}

# A function to print the default prior values
show_priors <- function(prior){
          cat("========== EZBHDDM Priors: ==================\n")
          cat("Drift rate:\n")
          if(!is.null(prior$drift_mean_mean)){  # Simple hierarchical model
              cat("Drift Mean Mean:", prior$drift_mean_mean,"\n")
              cat("Drift Mean Std Dev:",prior$drift_mean_sdev,"\n")
              cat("Drift Std Dev Shape:",prior$drift_sdev_lower,"\n")
              cat("Drift Std Dev Scale:",prior$drift_sdev_upper,"\n")
          }else{  # Meta regression on the drift rate
              cat("Drift Intercept Mean:", prior$drift_intercept_mean,"\n")
              cat("Drift Intercept Std Dev:", prior$drift_intercept_sdev,"\n")
              cat("Drift Coefficient Mean:",prior$drift_coefficient_mean,"\n")
              cat("Drift Coefficient Std Dev:",prior$drift_coefficient_sdev,"\n")
              cat("Drift Error Shape:",prior$drift_sdev_lower,"\n")
              cat("Drift Error Scale:",prior$drift_sdev_upper,"\n")
          }
          cat("Bound distance:\n")
          cat("Bound Mean Mean:   ", prior$bound_mean_mean,"\n")
          cat("Bound Mean Std Dev:",prior$bound_mean_sdev,"\n")
          cat("Bound Std Dev Shape:",prior$bound_sdev_lower,"\n")
          cat("Bound Std Dev Scale:",prior$bound_sdev_upper,"\n")
          cat("Non-decision Time:\n")
          cat("Non-decision Time Mean Mean:",prior$nondt_mean_mean,"\n")
          cat("Non-decision Time Mean Std: ", prior$nondt_mean_sdev,"\n")
          cat("Non-decision Time Shape:",prior$nondt_sdev_lower,"\n")
          cat("Non-decision Time Scale:",prior$nondt_sdev_upper,"\n")
}

# A function to print the parameter values used to generate data used in the simulation.
show_parameters <- function(parameter_set){
          cat("===== EZBHDDM True Parameters: ==============\n")
          if(!is.null(parameter_set$drift_B0)){  # Simple hierarchical model
             cat("Drift Intercept:   ", parameter_set$drift_intercept,"\n")
             if(!is.null(parameter_set$drift_B1)){
                    cat("Drift Coefficient: ", parameter_set$drift_coefficient,"\n")
             }
             cat("Drift SD:          ", parameter_set$drift_sdev,"\n") 
          }else{
             cat("Drift Mean:   ", parameter_set$drift_mean,"\n")
             cat("Drift Error:     ", parameter_set$drift_sdev,"\n")             
          }
          cat("Bound Mean:   ", parameter_set$bound_mean,"\n")
          cat("Bound SD:     ", parameter_set$bound_sdev,"\n")
          cat("Non-decision Time Mean:", parameter_set$nondt_mean,"\n")
          cat("Non-decision Time SD:  ", parameter_set$nondt_sdev,"\n")
          cat("=============================================\n")
}
```

## Setup functions

1. `default_priors`: A function to load default prior values.
2. `sample_parameters`: A function to sample true parameter values from the priors specified.

```{r, echo=FALSE}
# A function to load the default prior values
default_priors <- function(Show=TRUE){
    prior <- data.frame("bound_mean_mean" = 1.50,
                        "bound_mean_sdev" = 0.20,
                        "drift_mean_mean" = 0.00,
                        "drift_mean_sdev" = 0.50,
                        "nondt_mean_mean" = 0.30,
                        "nondt_mean_sdev" = 0.06,
                        "bound_sdev_lower" = 0.10,
                        "bound_sdev_upper" = 0.20,
                        "drift_sdev_lower" = 0.20,
                        "drift_sdev_upper" = 0.40,
                        "nondt_sdev_lower" = 0.05,
                        "nondt_sdev_upper" = 0.1)
    if(Show){       show_priors(prior)           }
  return(prior)
}

# A function to sample true parameter values from the priors specified
sample_parameters <- function(settings, Show=TRUE){
    prior <- settings$prior
    bound_mean <- rnorm(1,prior$bound_mean_mean,prior$bound_mean_sdev)
    if(is.null(prior$drift_intercept_mean)){
          drift_mean <- rnorm(1,prior$drift_mean_mean,prior$drift_mean_sdev)
    }else{
          drift_mean <- 0
    }
    nondt_mean <- rnorm(1,prior$nondt_mean_mean,prior$nondt_mean_sdev)
    bound_sdev <- runif(1,prior$bound_sdev_lower,prior$bound_sdev_upper)  
    drift_sdev <- runif(1,prior$drift_sdev_lower,prior$drift_sdev_upper)
    nondt_sdev <- runif(1,prior$nondt_sdev_lower,prior$nondt_sdev_upper)
    bound <- rnorm(settings$nPart,bound_mean, bound_sdev)
    drift <- rnorm(settings$nPart,drift_mean, drift_sdev)
    nondt <- abs(rnorm(settings$nPart,nondt_mean, nondt_sdev))
    parameter_set <- list("bound_mean" = bound_mean, "drift_mean" = drift_mean, "nondt_mean" = nondt_mean, 
                          "bound_sdev" = bound_sdev, "drift_sdev" = drift_sdev, "nondt_sdev" = nondt_sdev,
                          "bound" = bound,   "drift" = drift,   "nondt" = nondt)
    if(Show){         show_parameters(parameter_set)              }
  return(parameter_set)
}
```

## Working with JAGS

1. `write_JAGSmodel`: A function to write the JAGS model using the prior values.
2. `data_toJAGS`: A function to create a list with all the data objects to be passed to JAGS.
3. `default_inits`:  A function to create an object containing initial values for the drift.
4. `extractSamples`: A function to extract all samples associated with a `parameter.name`
5. `getError`: A function to compute the difference between the true value and estimate retrieved for every parameter.
6. `check_Rhat`: A function to check the Rhats for a simulation



```{r, echo=FALSE}
# A function to write the JAGS model using the prior values
write_JAGSmodel <- function(prior, modelFile = "EZHBDDM.bug"){
      opening <- "model{"
      prior.bound_m <- paste("          bound_mean ~ dnorm(", prior$bound_mean_mean,",pow(",prior$bound_mean_sdev,",-2))T(0.10,3.00)", sep="")
      prior.nondt_m <- paste("          nondt_mean ~ dnorm(", prior$nondt_mean_mean,",pow(",prior$nondt_mean_sdev,",-2))T(0.05,1.00)", sep="")
      prior.bound_sd <- paste("          bound_sdev ~ dunif(", prior$bound_sdev_lower,",",prior$bound_sdev_upper,")", sep="")
      prior.nondt_sd <- paste("          nondt_sdev ~ dunif(", prior$nondt_sdev_lower,",",prior$nondt_sdev_upper,")", sep="")
      prior.drift_sd <- paste("          drift_sdev ~ dunif(", prior$drift_sdev_lower,",",prior$drift_sdev_upper,")", sep="")
      priors <- c(prior.bound_m, prior.nondt_m, prior.bound_sd, prior.nondt_sd, prior.drift_sd)
      if(!is.null(prior$drift_mean_mean)){
      prior.drift_m <- paste("          drift_mean ~ dnorm(", prior$drift_mean_mean,",pow(",prior$drift_mean_sdev,",-2))T(-3.00,3.00)", sep="")
      priors <- c(priors, prior.drift_m)
      }
      if(!is.null(prior$drift_intercept_mean)){
      prior.drift_i <- paste("          drift_intrcpt ~ dnorm(", prior$drift_intercept_mean,",pow(",prior$drift_intercept_sdev,",-2))T(-3.00,3.00)", sep="")
      priors <- c(priors, prior.drift_i)
      }
      if(!is.null(prior$drift_coefficient_mean)){
      prior.drift_c <- paste("          drift_coeff ~ dnorm(", prior$drift_coefficient_mean,",pow(",prior$drift_coefficient_sdev,",-2))T(-3.00,3.00)", sep="")
      priors <- c(priors, prior.drift_c)
      }
      
      content.init <-"
              # Sampling model
              for (p in 1:nParticipants){
                  bound[p] ~ dnorm(bound_mean, pow(bound_sdev, -2))T(0.10,3.00)
                  nondt[p] ~ dnorm(nondt_mean, pow(nondt_sdev, -2))T(0.05,1.00)"
      if(!is.null(prior$drift_intercept_mean)){
          content.mid <- "                  drift_mean = drift_intrcpt"
          if(!is.null(prior$drift_coefficient_mean)){
              content.mid <- paste(content.mid," + (drift_coeff * x[p])", sep="") 
          }
          content.init <- c(content.init,content.mid)
      }
      content.end <- "                  drift[p] ~ dnorm(drift_mean, pow(drift_sdev, -2))T(-3.00,3.00)
      
                  # Forward equations from EZ Diffusion
                  ey[p]  = exp(-bound[p] * drift[p])
                  Pc[p]  = 1 / (1 + ey[p])
                  PRT[p] = 2 * pow(drift[p], 3) / bound[p] * pow(ey[p] + 1, 2) / (2 * -bound[p] * drift[p] * ey[p] - ey[p]*ey[p] + 1)
                  MDT[p] = (bound[p] / (2 * drift[p])) * (1 - ey[p]) / (1 + ey[p])
                  MRT[p] = MDT[p] + nondt[p]

                  # Loss functions using MRT, PRT, and Pc
                  meanRT[p]  ~ dnorm(MRT[p], PRT[p] * correct[p])
                  varRT[p]   ~ dnorm(1/PRT[p], 0.5 * correct[p] * PRT[p] * PRT[p])
                  correct[p] ~ dbin(Pc[p], nTrialsPerPerson)
              }
      }"
      content <- c(content.init, content.end)

      final_file <- file(modelFile)
      writeLines(c(opening,priors,content), final_file)
      close(final_file)
}
```

```{r, echo=FALSE}
# A function to create a list with all the data objects in the JAGS model
data_toJAGS <- function(){
    passData <- list("nParticipants", "nTrialsPerPerson",
                     "meanRT", "varRT", "correct")
    return(passData)
}

default_inits <- function(n.chains,nParticipants){
  myinits <- rep(list(list()), n.chains)
  for(i in 1:n.chains){
      myinits[[i]] <- list(drift = rnorm(nParticipants,0,0.1))
  }
  return(myinits)
}

# A function to extract individual samples for any parameter
extractSamples <- function(parameter.name, samples){
        postParam.Array <- samples$BUGSoutput$sims.array
        samplesID <- names(postParam.Array[1,1,])
        locateParameter  <- which(grepl(parameter.name,samplesID))
        
        param.is.hierarchical <- length(which(grepl("_",parameter.name)))!=0
        if(!param.is.hierarchical){
          locateHierPar <- which(grepl("_",samplesID))
          locateParameter <- locateParameter[!locateParameter %in% locateHierPar]   
        }
        
        # Now, for individual/task level parameters...
        if(length(locateParameter)>1){
              # We isolate the pages ID that contain the parameter of interest
              samplesRelated <- samplesID[locateParameter]
              # We identify the maximum index
              locateParticipantID <-as.numeric(gsub("\\D", "", samplesRelated))
              nP <- max(locateParticipantID,na.rm = TRUE)
              # We locate the page ID containing the last index
              lastP <- which(grepl(nP,samplesRelated))
              # And isolate all IDs from there
              locateParameter <- samplesRelated[(lastP-nP)+1:lastP]
        }
        # We retrieve only the pages containing the parameter
        x <- postParam.Array[,,locateParameter]
return(x)
}


# A function to compute the difference between the true value and estimate retrieved for every parameter.
getError <- function(estimates, parameter_set){
  error <- list("bound" = estimates$bound - parameter_set$bound,
                "nondt" = estimates$nondt - parameter_set$nondt,
                "drift" = estimates$drift - parameter_set$drift,
                "bound_mean" = estimates$bound_mean - parameter_set$bound_mean,
                "bound_sdev" = estimates$bound_sdev - parameter_set$bound_sdev,
                "nondt_mean" = estimates$nondt_mean - parameter_set$nondt_mean,
                "nondt_sdev" = estimates$nondt_sdev - parameter_set$nondt_sdev,
                "drift_mean" = estimates$drift_mean - parameter_set$drift_mean,
                "drift_sdev" = estimates$drift_sdev - parameter_set$drift_sdev)
  return(error)
}

# A function to check the Rhats for a simulation
check_Rhat <- function(simOutput){
      rule <- 1.05
      rhats <-simOutput$sim_rhats
      bad.Rhat <- which(rhats>rule,arr.ind = TRUE)
      test.rhat <- length(bad.Rhat) > 0
      if(!test.rhat){
        par(mfrow=c(1,1))
        bad.Rhat.ID <- colnames(rhats)[bad.Rhat[,2]]
    
        hist(rhats[which(rhats>rule)],
             main=paste("Rhats > or = than ", rule))
        abline(v=rule, col="red", lty=2)
        legend("top",paste("Rhat = ",rule," | ",
                           (round(nrow(bad.Rhat)/prod(dim(rhats)),5))*100,
                           "% of chains | ", length(bad.Rhat.ID), " chains", sep=""), lty=2, col="red", cex=0.4)
        table(bad.Rhat.ID)
      }else{
        paste("No Rhat greater than ", rule, sep="")      
      }
}
```

## Plotting functions
8. `plot.Chain`: A function to plot the merging chains for hierarchical parameters

```{r}
# A function to plot the merging chains for hierarchical parameters
plot.Chain <- function(samples){
    posterior.samples <- samples$BUGSoutput$sims.array
    labels <- names(posterior.samples[1,1,])
    locateHier <- which(grepl("_",labels))
    N <- length(locateHier)
    n.chains <- ncol(posterior.samples[,,labels[locateHier[1]]])
    par(mfrow = c(2, 3), mar =c(5.1,2,4.1,2), bty = "o")
    for(i in locateHier){
        plot(posterior.samples[,1,i], type="l", main=labels[i], 
             xlab="Iteration", ylab="Value sampled")  
        if(n.chains>1){
             for(a in 2:n.chains){
             lines(posterior.samples[,a,i],col=a)
             }
          }
    }
}

recoveryPlot <- function(x.true, y.estimated, parameterName){
  allValues <- c(x.true,y.estimated)
  param.is.bound <- length(which(grepl("ound",parameterName)))!=0
  param.is.nondt <- length(which(grepl("no",parameterName)))!=0
  if(param.is.bound){   color <- "blueviolet"
                        ax.lim <- c(0.5,2.5)
  }else{if(param.is.nondt){   color <- "dodgerblue4"
                              ax.lim <- c(0,0.75)
  }else{  color <- "goldenrod4"
          ax.lim <- c(-2,2)
  }}
  par(bty="o")
  plot(x.true,y.estimated, ann=F, col=color, pch=16,
       xlim=ax.lim, ylim=ax.lim)
  abline(0,1, lty=2)
  mtext("Simulated values", 1, line=2.1, cex=0.7)
  mtext(parameterName, 3, line=0.5, cex=0.8, f=2)
}

showRecovery <- function(simStudy, nParticipants, nTrials){
  par(mfrow = c(2, 3))#, mar =c(5.1,2,4.1,2))
  x <- simStudy$sim_means
  recoveryPlot(x[,"true","drift_mean"],x[,"est","drift_mean"],"Group mean drift")
  recoveryPlot(x[,"true","bound_mean"],x[,"est","bound_mean"],"Group mean bound")
  recoveryPlot(x[,"true","nondt_mean"],x[,"est","nondt_mean"],"Group mean nondt")
  y <- simStudy$sim_indiv
  recoveryPlot(y[,"true","drift"],y[,"est","drift"],"Individual drifts")
  recoveryPlot(y[,"true","bound"],y[,"est","bound"],"Individual bounds")
  recoveryPlot(y[,"true","nondt"],y[,"est","nondt"],"Individual nondt")
  title <- paste(nParticipants, " participants, ", nTrials, " trials each")
mtext(title, side = 3, line =-1.7, outer = TRUE, f=2, col="red3")
}
```

\clearpage

## Core functions

```{r}
# Sample data using simulation settings and true parameter values sampled
sample_data <- function(settings, parameter_set){
  nObs <- settings$nPart*settings$nTrials
  data <- matrix(NA,ncol=3,nrow=nObs)
  data[,1] <- rep(1:settings$nPart, each=settings$nTrials)
  for(i in 1:settings$nP){      # Get data for every Participant
      this.sub <- which(data[,1]==i)
      accuracy = 0
      while(sum(accuracy)==0){
            temp <- wdmrnd(a = parameter_set$bound[i], v = parameter_set$drift[i], 
                           t = parameter_set$nondt[i], n = settings$nTrials)
            accuracy = temp$accuracy
      }
      data[this.sub,3] <- accuracy
      data[this.sub,2] <- temp$RT
  }
  data <- as.data.frame(data)
  colnames(data) <- c("sub", "rt", "accuracy")
  return(data)
}

# Get individual statistics from raw data: mean accuracy and mean and variance of correct-RT
get_Statistics <- function(data){
  if(is.null(data$accuracy)|is.null(data$rt)){
        error.msg = "Data not available."
        return(print(error.msg))
    }
  subID <- unique(data$sub)
  sum_correct <- tapply(data$accuracy, data$sub, sum)  
  # Remove participants with no correct answer
  always_0 <- which(sum_correct==0)
  if(length(always_0)!=0){
        bad_participants <- (data$sub %in% always_0)
        data <- data[-bad_participants,]
        sum_correct <- tapply(data$accuracy, data$sub, sum) 
  }
  # Get proportion of correct responses
  mean_accuracy <- tapply(data$accuracy, data$sub, mean) 
  # Get mean and variance of correct RT
  keep.correct <- which(data$accuracy==1)
  correct_only <- data[keep.correct,]
  mean_rt_correct <- tapply(correct_only$rt, correct_only$sub, mean)
  var_rt_correct  <- tapply(correct_only$rt, correct_only$sub, var)
  # Create a data.frame with just summary statistics
  data_statistics <- cbind(subID, sum_correct, mean_accuracy, mean_rt_correct, var_rt_correct)
  data_statistics <- as.data.frame(data_statistics)
  colnames(data_statistics) = c("sub", "sum_correct","meanAccuracy", "meanRT_correct", "varRT_correct")
  return(data_statistics)
}
```

## Main functions

```{r}
# A function to load priors and true values to use in simulation
Hddm_Parameter_Set <-function(nParticipants, nTrials, Show=TRUE){
    if(Show){  design_summary(nParticipants,nTrials)  }
    prior <- default_priors(Show)
    settings <- list("nPart"= nParticipants, "nTrials"= nTrials, "prior"= prior)
    parameter_set <- sample_parameters(settings, Show)
    return(list("settings" = settings, "parameter_set" = parameter_set))
}

# A function to generate raw data, summary statistics and data to be passed on JAGS
Hddm_Data <- function(settings, parameter_set){
    rawData = sample_data(settings,parameter_set)
    sumData = get_Statistics(rawData)
    jagsData = data_toJAGS()
    return(list("rawData" = rawData, "sumData" = sumData, "jagsData" = jagsData))
}

# A function to run JAGS model
Hddm_runJAGS <- function(getData, settings, n.chains, modelFile="./EZHBDDM.bug", plot.Chains = FALSE){
    # Write model
    write_JAGSmodel(settings$prior)
    # Load settings
    parameters <- c("bound_mean", "drift_mean", "nondt_mean", "bound", "nondt",
                    "drift_sdev", "nondt_sdev", "bound_sdev", "drift")
    myinits    <- default_inits(n.chains, settings$nPart)
    data <- getData$jagsData
    # Prepare data
    sub     <- getData$sumData$sub
    correct <- getData$sumData$sum_correct
    varRT   <- getData$sumData$varRT_correct
    meanRT  <- getData$sumData$meanRT_correct
    nTrialsPerPerson <- as.numeric(unique(tapply(getData$rawData$accuracy,getData$rawData$sub,length)))
    nParticipants    <- length(getData$sumData$sub)
    # Run model and get samples
    suppressMessages(library(R2jags))
    suppressMessages(samples <- jags(data=data, 
                                parameters.to.save=parameters, 
                                model=modelFile, 
                                n.chains=n.chains, 
                                n.iter=4000, 
                                n.burnin=200, 
                                n.thin=1, 
                                DIC=T, 
                                inits=myinits))
    if(plot.Chains){  plot.Chain(samples)   }
    
    object <- samples$BUGSoutput$sims.array
    Rhats <- apply(object,3,Rhat)
return(list("estimates" = list("drift" = apply(extractSamples("drift", samples),3,mean), 
                              "drift_mean" = mean(extractSamples("drift_mean", samples)),
                              "drift_sdev" = mean(extractSamples("drift_sdev", samples)),  
                              "bound" = apply(extractSamples("bound", samples),3,mean), 
                              "bound_mean" = mean(extractSamples("bound_mean", samples)),
                              "bound_sdev" = mean(extractSamples("bound_sdev", samples)),
                              "nondt" = apply(extractSamples("nondt", samples),3,mean), 
                              "nondt_mean" = mean(extractSamples("nondt_mean", samples)),
                              "nondt_sdev" = mean(extractSamples("nondt_sdev", samples))),
            "rhats" = Rhats))
}

# Main function: A function to run a complete simulation for nParticipants and nTrials per participant
Hddm_runSim <- function(nParticipants, nTrials, n.chains = 4, Show=TRUE){
      design.parameters <- Hddm_Parameter_Set(nParticipants,nTrials, Show=Show)
      settings <- design.parameters$settings
      parameter_set <- design.parameters$parameter_set
      getData <- Hddm_Data(settings,parameter_set)
      runJags <- Hddm_runJAGS(getData=getData, n.chains = n.chains, settings = settings)
      estimates <- runJags$estimates
      error <- getError(estimates, parameter_set)
return(list("values" = list("trueValues" = parameter_set, "estValues" = estimates, "error" = error),
            "rhats"  = runJags$rhats))
}


Hddm_simStudy <- function(nSim, nParticipants, nTrials, n.chains = 4,
                          Show=FALSE, forceSim = FALSE){
    outputFile <- nameOutput(nTrials, nParticipants)
    runSim <- TRUE
    
    design.parameters <- Hddm_Parameter_Set(nParticipants,nTrials)
    parameter_set <- design.parameters$parameter_set
    nPar <- sum(lapply(parameter_set, length) > 1)
    no.Rhats  <- (nParticipants*nPar)+(length(parameter_set)-nPar)+1
    
    if((!forceSim)&(file.exists(outputFile))){runSim <- FALSE}
    if(runSim){
      # Empty arrays to store hierarchical and individual parameters
      # Pages = Parameter | Rows = Point values | Cols = True/Estimated/Error
      sim_means <- array(NA, dim=c(nSim,3,nPar))
      sim_indiv <- array(NA, dim=c(nSim*nParticipants,3,nPar))
      sim_rhats <- array(NA, dim=c(nSim,no.Rhats))
      indiv_init = 1
      for(k in 1:nSim){
          set.seed(k)
          cat("Iteration", k, "of", nSim,"\n")
          tryCatch({
            runSim <- Hddm_runSim(nParticipants = nParticipants, nTrials = nTrials, Show = FALSE)
            sim <- runSim$values
            rhats <- runSim$rhats
            sim_rhats[k,]   <- runSim$rhats
            sim_means[k,,1] <- c(sim$trueValues$drift_mean, sim$estValues$drift_mean, sim$error$drift_mean)
            sim_means[k,,2] <- c(sim$trueValues$bound_mean, sim$estValues$bound_mean, sim$error$bound_mean)
            sim_means[k,,3] <- c(sim$trueValues$nondt_mean, sim$estValues$nondt_mean, sim$error$nondt_mean)
            Last = nParticipants*k
            sim_indiv[indiv_init:Last,,1] = c(sim$trueValues$drift, sim$estValues$drift, sim$error$drift)
            sim_indiv[indiv_init:Last,,2] = c(sim$trueValues$bound, sim$estValues$bound, sim$error$bound)
            sim_indiv[indiv_init:Last,,3] = c(sim$trueValues$nondt, sim$estValues$nondt, sim$error$nondt)
            indiv_init = Last + 1        
            }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
      }
      sim_means <- sim_means[which(!is.na(sim_means[,1,1])),,]
      sim_indiv <- sim_indiv[which(!is.na(sim_indiv[,1,1])),,]
      dimnames(sim_means) <- list(NULL, c("true","est","error"), c("drift_mean","bound_mean","nondt_mean"))
      dimnames(sim_indiv) <- list(NULL, c("true","est","error"), c("drift","bound","nondt"))
      colnames(sim_rhats) <- names(rhats)
      simOutput = list("sim_means" = sim_means, "sim_indiv" = sim_indiv, "sim_rhats" = sim_rhats)
      save(simOutput,file=outputFile)
    }else{    load(outputFile)     }
    return(simOutput)
}
```

\clearpage


\begin{align*}
\mathbf{Y}_{ik} &\sim \mbox{DDM}(\nu_i, \alpha_{i}, \tau_{i}) \\
\nu_i &\sim \mbox{N}(\mu_\nu, \sigma_\nu)\\
\alpha_i &\sim \mbox{N}(\mu_\alpha, \sigma_\alpha)\\
\tau_i &\sim \mbox{N}(\mu_\tau, \sigma_\tau)
\end{align*}

```{r}
cat(readLines('./EZHBDDM.bug'), sep = '\n')
```

# Run simple example


```{r}
sim <- Hddm_runSim(nParticipants = 100, nTrials = 200)
```

\vspace{-0.5in}

```{r, echo=FALSE, fig.height=3, fig.align='center'}
par(mfrow = c(1, 3), mar =c(5.1,2,4.1,2))
recoveryPlot(sim$values$trueValues$drift,sim$values$estValues$drift, "Individual drift")
recoveryPlot(sim$values$trueValues$bound,sim$values$estValues$bound, "Individual bound")
recoveryPlot(sim$values$trueValues$nondt,sim$values$estValues$nondt, "Individual nondt")
```



\clearpage

\vspace{5in}

# Full smulation studies (200 repetitions)

\vspace{.75in}

## 150 trials

```{r}
nSim <- 200

nT <- 150
nP1 <- 10
nP2 <- 80
nP3 <- 200
nP4 <- 500
```

```{r, results='hide',message=FALSE}
simStudy1 <- Hddm_simStudy(nSim = nSim, nParticipants = nP1, nTrials = nT)
#simStudy2 <- Hddm_simStudy(nSim = nSim, nParticipants = nP2, nTrials = nT)
# simStudy3 <- Hddm_simStudy(nSim = nSim, nParticipants = nP3, nTrials = nT)
# simStudy4 <- Hddm_simStudy(nSim = nSim, nParticipants = nP4, nTrials = nT)
```

```{r}

```
\vspace{.75in}

## 150 participants

```{r}
nSim <- 200

nP <- 150
nT1 <- 10
nT2 <- 80
nT3 <- 200
nT4 <- 500
```

```{r, results='hide',message=FALSE}
# simStudy5 <- Hddm_simStudy(nSim = nSim, nParticipants = nP, nTrials = nT1)
# simStudy6 <- Hddm_simStudy(nSim = nSim, nParticipants = nP, nTrials = nT2)
# simStudy7 <- Hddm_simStudy(nSim = nSim, nParticipants = nP, nTrials = nT3)
# #simStudy8 <- Hddm_simStudy(nSim = nSim, nParticipants = nP, nTrials = nT4)
```


\clearpage

```{r, message=FALSE, results='hide', echo=FALSE, fig.align='center'}
showRecovery(simStudy1, nP1, nT)
```

```{r, message=FALSE, results='hide', echo=FALSE, fig.align='center'}
showRecovery(simStudy2, nP2, nT)
```

```{r, message=FALSE, results='hide', echo=FALSE, fig.align='center'}
showRecovery(simStudy3, nP3, nT)
```

```{r, message=FALSE, results='hide', echo=FALSE, fig.align='center'}
showRecovery(simStudy4, nP4, nT)
```

\clearpage

```{r, message=FALSE, results='hide', echo=FALSE, fig.align='center'}
showRecovery(simStudy5, nP, nT1)
```


```{r, message=FALSE, results='hide', echo=FALSE, fig.align='center'}
showRecovery(simStudy6, nP, nT2)
```


```{r, message=FALSE, results='hide', echo=FALSE, fig.align='center'}
showRecovery(simStudy7, nP, nT3)
```


```{r, message=FALSE, results='hide', echo=FALSE, fig.align='center'}
#showRecovery(simStudy8, nP, nT4)
```
\clearpage

# Meta Regression

-------------------

\begin{align*}
\mathbf{Y}_{ik} &\sim \mbox{DDM}(\delta_{i}, \eta_i, \tau_{i}) \\
\textcolor{red}{\delta_i &\sim \mbox{N}(\beta_0 + \beta_1x_i, \sigma_\delta)\\}
\eta_i &\sim \mbox{N}(\mu_\eta, \sigma_\eta)\\
\tau_i &\sim \mbox{N}(\mu_\tau, \sigma_\tau)
\end{align*}

# Function tunning

The code for the auxiliary functions listed below is hidden from this pdf file (but can be checked on the .Rmd). 

1. `getCovariates`: A function to obtain a list of random covariates (i.e. real numbers vs indicator variables)
2. `default_priors2`: A function to load and print default prior values. 
3. `sample_parameters`: A function to sample true parameter values from the priors specified. 
4. `write_JAGSmodel`: A function to write the JAGS model using the prior values.
5. `data_toJAGS`: A function to create a list with all the data objects to be passed to JAGS.
6. `default_inits`:  A function to create an object containing initial values for the drift.
7. `extractSamples`: A function to extract all samples associated with a `parameter.name`
8. `plot.Chain`: A function to plot the merging chains for hierarchical parameters
9. `getError`: A function to compute the difference between the true value and estimate retrieved for every parameter.
10. `nameOutput` : A function to generate an appropriate output name based on the number of trials and participants


```{r, echo=FALSE}
# A function to obtain a list of random covariates (i.e., real numbers or indicator variables)
getCovariates<- function(n, mean, sd, n.indexes=NA){
    if(is.na(n.indexes)){   # Covariate is a real number
          x <- rnorm(n,mean, sd)
    }else{     # Covariate is an indicative variable
          if(n.indexes==2){
                x <- rbinom(n,1,0.5)
          }else{
                p <- rep(1/n.indexes,n.indexes) 
                y <- rmultinom(n,1,p)
                x <- rep(0,n)
                for(i in 1:n.indexes){
                    x[y[i,]==1] <- i
                }
          }
    }
  return(x)
}
 
# A function to load and print default prior values
default_priors2 <- function(Show=TRUE){
     prior <- default_priors(Show=FALSE)   # Load regular priors
     prior$drift_mean_mean <- NULL       # Remove drift hierarchical distribution
     prior$drift_mean_sdev <- NULL
     prior$drift_intercept_mean <- 1.50  # Add a prior for the intercept and coefficients
     prior$drift_intercept_sdev <- 0.20
     prior$drift_coefficient_mean <- 0.00
     prior$drift_coefficient_sdev <- 0.50
     if(Show){
           show_priors(prior)
     }
   return(prior)
}

# A function to sample true parameter values from the priors specified
sample_parameters2 <- function(x, settings, parameter_set, Show=TRUE){
    prior <- settings$prior
    drift_B0 <- rnorm(1,prior$drift_intercept_mean,prior$drift_intercept_sdev)
    drift_B1 <- rnorm(1,prior$drift_coefficient_mean,prior$drift_coefficient_sdev)
    drift_mean <- drift_B0+(drift_B1*x)
    parameter_set$drift_intercept <- drift_B0
    parameter_set$drift_coefficient <- drift_B1
    parameter_set$drift_mean <- drift_mean
    parameter_set$drift <- rnorm(settings$nPart,drift_mean, drift_sdev)
    if(Show){     show_parameters(parameter_set)      }
  return(parameter_set)
}


# A function to create a list with all the data objects in the JAGS model
data_toJAGS <- function(){
    passData <- list("nParticipants", "nTrialsPerPerson",
                     "meanRT", "varRT", "correct")
    return(passData)
}

default_inits <- function(n.chains,nParticipants){
  myinits <- rep(list(list()), n.chains)
  for(i in 1:n.chains){
      myinits[[i]] <- list(drift = rnorm(nParticipants,0,0.1))
  }
  return(myinits)
}


# A function to compute the difference between the true value and estimate retrieved for every parameter.
getError <- function(estimates, parameter_set){
  error <- list("bound" = estimates$bound - parameter_set$bound,
                "nondt" = estimates$nondt - parameter_set$nondt,
                "drift" = estimates$drift - parameter_set$drift,
                "bound_mean" = estimates$bound_mean - parameter_set$bound_mean,
                "bound_sdev" = estimates$bound_sdev - parameter_set$bound_sdev,
                "nondt_mean" = estimates$nondt_mean - parameter_set$nondt_mean,
                "nondt_sdev" = estimates$nondt_sdev - parameter_set$nondt_sdev,
                "drift_mean" = estimates$drift_mean - parameter_set$drift_mean,
                "drift_sdev" = estimates$drift_sdev - parameter_set$drift_sdev)
  return(error)
}
```

## Plotting functions

```{r}
# recoveryPlot <- function(x.true, y.estimated, parameterName){
#   allValues <- c(x.true,y.estimated)
#   param.is.bound <- length(which(grepl("ound",parameterName)))!=0
#   param.is.nondt <- length(which(grepl("no",parameterName)))!=0
#   if(param.is.bound){   color <- "blueviolet"
#   }else{if(param.is.nondt){   color <- "dodgerblue4"
#   }else{  color <- "goldenrod4" }}
#   par(bty="o")
#   plot(x.true,y.estimated, ann=F, col=color, pch=16,
#        xlim=c(min(allValues),max(allValues)),
#        ylim=c(min(allValues),max(allValues)))
#   abline(0,1, lty=2)
#   mtext("Simulated values", 1, line=2.1, cex=0.7)
#   mtext(parameterName, 3, line=0.5, cex=0.8, f=2)
# }
# 
# showRecovery <- function(simStudy, nParticipants, nTrials){
#   par(mfrow = c(2, 3))#, mar =c(5.1,2,4.1,2))
#   x <- simStudy$sim_means
#   recoveryPlot(x[,"true","drift_mean"],x[,"est","drift_mean"],"Group mean drift")
#   recoveryPlot(x[,"true","bound_mean"],x[,"est","bound_mean"],"Group mean bound")
#   recoveryPlot(x[,"true","nondt_mean"],x[,"est","nondt_mean"],"Group mean nondt")
#   y <- simStudy$sim_indiv
#   recoveryPlot(y[,"true","drift"],y[,"est","drift"],"Individual drifts")
#   recoveryPlot(y[,"true","bound"],y[,"est","bound"],"Individual bounds")
#   recoveryPlot(y[,"true","nondt"],y[,"est","nondt"],"Individual nondt")
#   title <- paste(nParticipants, " participants, ", nTrials, " trials each")
# mtext(title, side = 3, line =-1.7, outer = TRUE, f=2, col="red3")
# }
```

## Core functions

```{r}
# Sample data using simulation settings and true parameter values sampled
# sample_data <- function(settings, parameter_set){
#   nObs <- settings$nPart*settings$nTrials
#   data <- matrix(NA,ncol=3,nrow=nObs)
#   data[,1] <- rep(1:settings$nPart, each=settings$nTrials)
#   for(i in 1:settings$nP){      # Get data for every Participant
#       this.sub <- which(data[,1]==i)
#       accuracy = 0
#       while(sum(accuracy)==0){
#             temp <- wdmrnd(a = parameter_set$bound[i], v = parameter_set$drift[i], 
#                            t = parameter_set$nondt[i], n = settings$nTrials)
#             accuracy = temp$accuracy
#       }
#       data[this.sub,3] <- accuracy
#       data[this.sub,2] <- temp$RT
#   }
#   data <- as.data.frame(data)
#   colnames(data) <- c("sub", "rt", "accuracy")
#   return(data)
# }
# 
# # Get individual statistics from raw data: mean accuracy and mean and variance of correct-RT
# get_Statistics <- function(data){
#   if(is.null(data$accuracy)|is.null(data$rt)){
#         error.msg = "Data not available."
#         return(print(error.msg))
#     }
#   subID <- unique(data$sub)
#   sum_correct <- tapply(data$accuracy, data$sub, sum)  
#   # Remove participants with no correct answer
#   always_0 <- which(sum_correct==0)
#   if(length(always_0)!=0){
#         bad_participants <- (data$sub %in% always_0)
#         data <- data[-bad_participants,]
#         sum_correct <- tapply(data$accuracy, data$sub, sum) 
#   }
#   # Get proportion of correct responses
#   mean_accuracy <- tapply(data$accuracy, data$sub, mean) 
#   # Get mean and variance of correct RT
#   keep.correct <- which(data$accuracy==1)
#   correct_only <- data[keep.correct,]
#   mean_rt_correct <- tapply(correct_only$rt, correct_only$sub, mean)
#   var_rt_correct  <- tapply(correct_only$rt, correct_only$sub, var)
#   # Create a data.frame with just summary statistics
#   data_statistics <- cbind(subID, sum_correct, mean_accuracy, mean_rt_correct, var_rt_correct)
#   data_statistics <- as.data.frame(data_statistics)
#   colnames(data_statistics) = c("sub", "sum_correct","meanAccuracy", "meanRT_correct", "varRT_correct")
#   return(data_statistics)
# }
```

## Main functions

```{r}
# A function to load priors and true values to use in simulation
# Hddm_Parameter_Set <-function(nParticipants, nTrials, Show=TRUE){
#     if(Show){  design_summary(nParticipants,nTrials)  }
#     prior <- default_priors(Show)
#     settings <- list("nPart"= nParticipants, "nTrials"= nTrials, "prior"= prior)
#     parameter_set <- sample_parameters(settings, Show)
#     return(list("settings" = settings, "parameter_set" = parameter_set))
# }
# 
# # A function to generate raw data, summary statistics and data to be passed on JAGS
# Hddm_Data <- function(settings, parameter_set){
#     rawData = sample_data(settings,parameter_set)
#     sumData = get_Statistics(rawData)
#     jagsData = data_toJAGS()
#     return(list("rawData" = rawData, "sumData" = sumData, "jagsData" = jagsData))
# }
# 
# # A function to run JAGS model
# Hddm_runJAGS <- function(getData, settings, n.chains, modelFile="./EZHBDDM.bug", plot.Chains = FALSE){
#     # Write model
#     write_JAGSmodel(settings$prior)
#     # Load settings
#     parameters <- c("bound_mean", "drift_mean", "nondt_mean", "bound", "nondt",
#                     "drift_sdev", "nondt_sdev", "bound_sdev", "drift")
#     myinits    <- default_inits(n.chains, settings$nPart)
#     data <- getData$jagsData
#     # Prepare data
#     sub     <- getData$sumData$sub
#     correct <- getData$sumData$sum_correct
#     varRT   <- getData$sumData$varRT_correct
#     meanRT  <- getData$sumData$meanRT_correct
#     nTrialsPerPerson <- as.numeric(unique(tapply(getData$rawData$accuracy,getData$rawData$sub,length)))
#     nParticipants    <- length(getData$sumData$sub)
#     # Run model and get samples
#     suppressMessages(library(R2jags))
#     suppressMessages(samples <- jags(data=data, 
#                                 parameters.to.save=parameters, 
#                                 model=modelFile, 
#                                 n.chains=n.chains, 
#                                 n.iter=1000, 
#                                 n.burnin=200, 
#                                 n.thin=1, 
#                                 DIC=T, 
#                                 inits=myinits))
#     if(plot.Chains){  plot.Chain(samples)   }
# return(list("drift" = apply(extractSamples("drift", samples),3,mean), 
#             "drift_mean" = mean(extractSamples("drift_mean", samples)),
#             "drift_sdev" = mean(extractSamples("drift_sdev", samples)),  
#             "bound" = apply(extractSamples("bound", samples),3,mean), 
#             "bound_mean" = mean(extractSamples("bound_mean", samples)),
#             "bound_sdev" = mean(extractSamples("bound_sdev", samples)),
#             "nondt" = apply(extractSamples("nondt", samples),3,mean), 
#             "nondt_mean" = mean(extractSamples("nondt_mean", samples)),
#             "nondt_sdev" = mean(extractSamples("nondt_sdev", samples))))
# }
# 
# # Main function: A function to run a complete simulation for nParticipants and nTrials per participant
# Hddm_runSim <- function(nParticipants, nTrials, n.chains = 4, Show=TRUE){
#       design.parameters <- Hddm_Parameter_Set(nParticipants,nTrials, Show=Show)
#       settings <- design.parameters$settings
#       parameter_set <- design.parameters$parameter_set
#       getData <- Hddm_Data(settings,parameter_set)
#       estimates <- Hddm_runJAGS(getData=getData, n.chains = n.chains, settings = settings)
#       error <- getError(estimates, parameter_set)
# return(list("trueValues" = parameter_set, "estValues" = estimates, "error" = error))
# }
# 
# 
# Hddm_simStudy <- function(nSim, nParticipants, nTrials, n.chains = 4,
#                           Show=FALSE, forceSim = FALSE){
#     outputFile <- nameOutput(nTrials, nParticipants)
#     runSim <- TRUE
#     nPar <- 3  # No. parameters: Drift, boundary, ndt
#     if((!forceSim)&(file.exists(outputFile))){runSim <- FALSE}
#     if(runSim){
#       # Empty arrays to store hierarchical and individual parameters
#       # Pages = Parameter | Rows = Point values | Cols = True/Estimated/Error
#       sim_means <- array(NA, dim=c(nSim,3,nPar))
#       sim_indiv <- array(NA, dim=c(nSim*nParticipants,3,nPar))
#       indiv_init = 1
#       for(k in 1:nSim){
#           set.seed(k)
#           cat("Iteration", k, "of", nSim,"\n")
#           tryCatch({
#             sim <- Hddm_runSim(nParticipants = nParticipants, nTrials = nTrials, Show = FALSE)
#             sim_means[k,,1] <- c(sim$trueValues$drift_mean, sim$estValues$drift_mean, sim$error$drift_mean)
#             sim_means[k,,2] <- c(sim$trueValues$bound_mean, sim$estValues$bound_mean, sim$error$bound_mean)
#             sim_means[k,,3] <- c(sim$trueValues$nondt_mean, sim$estValues$nondt_mean, sim$error$nondt_mean)
#             Last = nParticipants*k
#             sim_indiv[indiv_init:Last,,1] = c(sim$trueValues$drift, sim$estValues$drift, sim$error$drift)
#             sim_indiv[indiv_init:Last,,2] = c(sim$trueValues$bound, sim$estValues$bound, sim$error$bound)
#             sim_indiv[indiv_init:Last,,3] = c(sim$trueValues$nondt, sim$estValues$nondt, sim$error$nondt)
#             indiv_init = Last + 1        
#             }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
#       }
#       sim_means <- sim_means[which(!is.na(sim_means[,1,1])),,]
#       sim_indiv <- sim_indiv[which(!is.na(sim_indiv[,1,1])),,]
#       dimnames(sim_means) <- list(NULL, c("true","est","error"), c("drift_mean","bound_mean","nondt_mean"))
#       dimnames(sim_indiv) <- list(NULL, c("true","est","error"), c("drift","bound","nondt"))
#       simOutput = list("sim_means" = sim_means, "sim_indiv" = sim_indiv)
#       save(simOutput,file=outputFile)
#     }else{    load(outputFile)     }
#     return(simOutput)
# }
```

\clearpage

# Run simple example


```{r}
# sim <- Hddm_runSim(nParticipants = 50, nTrials = 150)
```





\[
\begin{align*}
\mathbf{Y}_{ijk} &\sim \mbox{DDM}(\delta_{ij}, \eta_{i}, \tau_i) \\
\delta_{ij} &= \beta_0 + \beta_1x_i + \beta_2y_j
\end{align*}
\]

```{r, echo=FALSE}
# #
# getCovariates_perCondition <- function(nCondition, mean, sd){
#     x <- rnorm(nCondition,mean, sd)
#     return(x)
# }
```