---
title: "EZBHDDM: Short report"
author: "Adriana F. Chávez De la Peña"
date: "`r Sys.Date()`"
output:
  rmdformats::material:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: true
    cards: false
    highlight: tango
    fig_width: 12 
    fig_height: 8 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(rmdformats)
```

# Introduction

\begin{align*}
\mathbf{Y} \sim \mbox{DDM}\bigl(\alpha, \nu, \tau \bigl)
\end{align*}

## The EZBHDDM

\begin{align*}
Y &\Rightarrow \{\dot{T}, \dot{M}, \dot{V}\}\\
\dot{T} &\sim \mbox{Binomial}(PC,N)\\
\dot{V} &\sim \mbox{Normal}(\frac{1}{PRT},\frac{N-1}{2(PRT)^2})\\
\dot{M} &\sim \mbox{Normal}(MRT, PRT \times N)\\
PC &= \frac{1}{\exp(-\alpha\nu)+1}\\
MRT &= \tau + \frac{\alpha}{2\nu}\frac{\exp(-\alpha\nu)-1}{\exp(-\alpha\nu)+1}\\
PRT &= \frac{\alpha}{2\nu^3}\{\frac{1-2\alpha\nu\exp(-\alpha\nu)-\exp(-\alpha\nu)^2}{(\exp(-\alpha\nu)+1)^2}\}
\end{align*}

# General setup

```{r}
for(archive in dir("./code/functions/")){    source(paste("./code/functions/",archive,sep=""))     }
for(archive in dir("./code/scripts/")){      source(paste("./code/scripts/",archive,sep=""))       }
```

```{r}
nParticipants <- 30
nTrials <- 300
nDatasets <- 50
```

# Hierarchical model

```{r, eval=FALSE}
simH <- HDDM_runSims(nParticipants, nTrials, nDatasets, modelType = "hierarchical")
```

```{r, echo=FALSE}
suppressWarnings(setwd("./simulations/simple_examples/"))
simH <- HDDM_runSims(nParticipants = nParticipants, nTrials = nTrials, 
                     nDatasets = nDatasets, modelType = "hierarchical")
check_Rhat(simH$rhats)
```

```{r, echo=FALSE, fig.height=4, fig.align='center'}
plot_recovery(simH)
```

# Metaregression model

```{r, eval=FALSE}
simM <- HDDM_runSims(nParticipants, nTrials, nDatasets, modelType = "metaregression")
```

```{r, echo=FALSE}
setwd("./simulations/simple_examples/")
simM <- HDDM_runSims(nParticipants = nParticipants, nTrials = nTrials, 
                     nDatasets = nDatasets, modelType = "metaregression")
check_Rhat(simM$rhats)
```

```{r, echo=FALSE, fig.height=4, fig.align='center'}
plot_recovery(simM)
```

# T-test model

```{r, eval=FALSE}
simT <- HDDM_runSims(nParticipants, nTrials, nDatasets, modelType = "ttest")
```

```{r, echo=FALSE}
setwd("./simulations/simple_examples/")
simT <- HDDM_runSims(nParticipants = nParticipants, nTrials = nTrials, 
                     nDatasets = nDatasets, modelType = "ttest")
check_Rhat(simT$rhats)
```

```{r, results='hide',message=FALSE, eval=FALSE}
plot_recovery(simT)
```

```{r}
show_priors(priors)
```


```{r}
par(mfrow = c(3,2), mai=c(0,0,0,0))
b <- seq(0.1,3,0.01)
plot(b,dnorm(b,1.5,0.2))
plot(b,dnorm(b,1,0.1))
plot(b,dnorm(b,1,0.3))
plot(b,dnorm(b,2,0.1))
plot(b,dnorm(b,2,0.3))

par(mfrow = c(3,2), mai=c(0,0,0,0))
d <- seq(-3,3,0.01)
plot(d,dnorm(d,0,0.5))
plot(d,dnorm(d,-1.5,0.2))
plot(d,dnorm(d,-1.5,0.4))
plot(d,dnorm(d,1.5,0.2))
plot(d,dnorm(d,1.5,0.4))

par(mfrow = c(3,2), mai=c(0,0,0,0))
n <- seq(0.05,2,0.01)
plot(n, dnorm(n,0.3,0.06))
plot(n, dnorm(n,0.1,0.05))
plot(n, dnorm(n,0.5,0.05))
plot(n, dnorm(n,0.1,0.25))
plot(n, dnorm(n,0.5,0.25))
abline(v=0.1)

plot(seq(0.05,2,0.01), 
     dnorm(seq(0.05,2,0.01),0.1,0.1))
```


```{r, echo=FALSE}
for(archive in dir("./code/functions/")){   source(paste("./code/functions/",archive,sep=""))     }
setwd("./simulations/simple_examples/")
start <- Sys.time()
simM <- HDDM_runSims(nParticipants = 30, nTrials = 300, 
                     nDatasets = 100, modelType = "ttest", fromPrior = FALSE, forceSim = TRUE)
end <- Sys.time()
check_Rhat(simM$rhats)

end-start
plot_recovery(simM)
```
