---
title: "EZ Bayesian Hierarchical Drift Diffusion Model"
author: "Adriana F. Chavez De la Pena"
date: "Last time knitted: `r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=1cm,right=1cm,top=2cm,bottom=2cm"
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[L]{EZ Bayesian Hierarchical Drift Diffusion Model}
- \fancyfoot[LE,RO]{\thepage}
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

-------------------

# Basic functions to generate DDM data

\begin{align*}
\mathbf{Y} \sim \mbox{DDM}\bigl(\alpha, \nu, \tau \bigl)
\end{align*}

```{r generate-DDM-data, file="./code/functions/generate_data.R"}
```

# Example: Generate some data

```{r example-parameters}
a = 1.50
v = 0.00
t = 0.30
n = 10000

data <- wdmrnd(a, v, t, n)
```

```{r example-plot, echo=FALSE, fig.height=3.5, file="./code/scripts/plot_data.R"}
```

\clearpage

# Simulation Study functions and variables

The code for the functions listed below is hidden from this pdf file (but can be checked on the .Rmd). Here we present a list of what these functions are and what they do!

## Auxiliary functions

```{r, file="./code/functions/auxiliary.R", echo=FALSE}
```

```{r, file="./code/functions/show_designSettings.R"}
```

## Setup functions

1. `default_priors`: A function to load default prior values.
2. `sample_parameters`: A function to sample true parameter values from the priors specified.

```{r, file="./code/functions/generate_parameters.R", echo=FALSE}
```

## Working with JAGS
