---
title: "EZBHDDM: Directory of functions and scripts"
author: "Adriana F. Chávez De la Peña"
date: "`r Sys.Date()`"
output:
  rmdformats::material:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: true
    cards: false
    highlight: tango
    fig_width: 12 
    fig_height: 8 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(rmdformats)
```

# Introduction

\begin{align*}
\mathbf{Y} \sim \mbox{DDM}\bigl(\alpha, \nu, \tau \bigl)
\end{align*}

## The EZBHDDM

\begin{align*}
Y &\Rightarrow \{\dot{T}, \dot{M}, \dot{V}\}\\
\dot{T} &\sim \mbox{Binomial}(PC,N)\\
\dot{V} &\sim \mbox{Normal}(\frac{1}{PRT},\frac{N-1}{2(PRT)^2})\\
\dot{M} &\sim \mbox{Normal}(MRT, PRT \times N)\\
PC &= \frac{1}{\exp(-\alpha\nu)+1}\\
MRT &= \tau + \frac{\alpha}{2\nu}\frac{\exp(-\alpha\nu)-1}{\exp(-\alpha\nu)+1}\\
PRT &= \frac{\alpha}{2\nu^3}\{\frac{1-2\alpha\nu\exp(-\alpha\nu)-\exp(-\alpha\nu)^2}{(\exp(-\alpha\nu)+1)^2}\}
\end{align*}

## Model Types included in this template

1. `hierarchical`

2. `metaregression`

3. `ttest`

# Custom functions

## Simulation setup functions

```{r, echo=FALSE}
source("./functions/namingFunctions.R")
source("./functions/show_priors.R")
source("./functions/show_parameters.R")
source("./functions/show_design.R")
source("./functions/default_priors.R")
source("./functions/sample_parameters.R")
```

1. `default_priors()`: A function to load default prior values.
2. `sample_parameters()`: A function to sample true parameter values from the priors specified.

## Functions to interact with JAGS

```{r, echo=FALSE}
source("./functions/write_JAGSmodel.R")
source("./functions/data_toJAGS.R")
source("./functions/default_inits.R")
source("./functions/extractSamples.R")
source("./functions/getDifferences_TRUEvsEST.R")
source("./functions/check_Rhat.R")
source("./functions/plot_Chain.R")
```

1. `write_JAGSmodel()`: A function to write the JAGS model using the prior values.
2. `data_toJAGS()`: A function to create a list with all the data objects to be passed to JAGS.
3. `default_inits()`:  A function to create an object containing initial values for the drift.
4. `extractSamples()`: A function to extract all samples associated with a `parameter.name`
5. `getDifferences_TRUEvsEST()`: A function to compute the difference between the true value and estimate retrieved for every parameter.
6. `check_Rhat()`: A function to check the Rhats for a simulation
7. `plot_Chain()`: A function to plot the merging chains for hierarchical parameters


## Data managment functions

1. `generate_trial()`:
2. `generate_dataset()`:

```{r, echo=FALSE}
source("./functions/generate_trial.R")
source("./functions/generate_dataset.R")
source("./functions/sample_data.R")
source("./functions/getStatistics.R")
```

```{r example-parameters}
data <- generate_dataset(a=1.5, v=0, t=0.3, n=1000)
```

```{r example-plot, echo=FALSE, fig.height=5}
par(mfrow = c(1, 3), mar =c(5.1,2,4.1,2), bty = "o")

rt <- data$RT
accuracy <- data$accuracy

hist(rt[accuracy==1], ann=F, axes=F, breaks=50, col="lightgreen", border=NA)
mtext("Distribution of Reaction Times", 3, cex=0.65, line=0.5)
mtext("Reaction Time", 1, cex=0.6, line=2)
mtext("Count", 2, cex=0.6, line=1)
legend("topright", col="lightgreen", "Correct", pch=15, cex=0.7, bty="n")
axis(1,c(0:5),line=-0.7)

hist(rt[accuracy==0], ann=F, axes=F, breaks=50, col="indianred1", border=NA)
mtext("Distribution of Reaction Times", 3, cex=0.65, line=0.5)
mtext("Reaction Time", 1, cex=0.6, line=2)
mtext("Count", 2, cex=0.6, line=1)
legend("topright", col="indianred1", "Incorrect", pch=15, cex=0.7, bty="n")
axis(1,c(0:5),line=-0.7)

barplot(c(sum(1-accuracy),sum(accuracy)), ann=F, axes=F, col=c("red3","springgreen3"))
mtext("Accuracy Histogram", 3, cex=0.65, line=0.5)
mtext("Count", 2, cex=0.6, line=1)
axis(1,c(0.7,1.9),c("Incorrect","Correct"))
```

3. `sample_data()`:
4. `getStatistics()`:

## Plotting functions

```{r, echo=FALSE}
source("./functions/plot_recovery.R")
```

1. `plot_recovery()`:

# Scripts

## Hddm_setup()

```{r, echo=FALSE}
source("./scripts/HDDM_setup.R")
```

```{r, file="./scripts/HDDM_setup.R"}
```

## HDDM_runJAGS() 

```{r, echo=FALSE}
source("./scripts/HDDM_runJAGS.R")
```

```{r, file="./scripts/HDDM_runJAGS.R"}
```

## HDDM_runSims()

```{r, echo=FALSE}
source("./scripts/HDDM_runSims.R")
```


```{r, file="./scripts/HDDM_runSims.R"}
```

