---
title: "EZBHDDM: Simulation studies sampling from uniform distributions"
author: "Adriana F. Chávez De la Peña"
date: "`r Sys.Date()`"
output:
  rmdformats::material:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: true
    cards: false
    highlight: tango
    fig_width: 12 
    fig_height: 8 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(rmdformats)
```

# Introduction

\begin{align*}
\mathbf{Y} \sim \mbox{DDM}\bigl(\alpha, \nu, \tau \bigl)
\end{align*}

## The EZBHDDM

\begin{align*}
Y &\Rightarrow \{\dot{T}, \dot{M}, \dot{V}\}\\
\dot{T} &\sim \mbox{Binomial}(PC,N)\\
\dot{V} &\sim \mbox{Normal}(\frac{1}{PRT},\frac{N-1}{2(PRT)^2})\\
\dot{M} &\sim \mbox{Normal}(MRT, PRT \times N)\\
PC &= \frac{1}{\exp(-\alpha\nu)+1}\\
MRT &= \tau + \frac{\alpha}{2\nu}\frac{\exp(-\alpha\nu)-1}{\exp(-\alpha\nu)+1}\\
PRT &= \frac{\alpha}{2\nu^3}\{\frac{1-2\alpha\nu\exp(-\alpha\nu)-\exp(-\alpha\nu)^2}{(\exp(-\alpha\nu)+1)^2}\}
\end{align*}

# Load simple functions

```{r}
# Auxiliary functions
###########################
# Function to create a name based on the simulation settings
source("../../code/functions/namingFunctions.R")
# Functions to print information to the screen
source("../../code/functions/show_design.R")
source("../../code/functions/show_parameters.R")
source("../../code/functions/show_priors.R")

# Functions to simulate data
##############################
source("../../code/functions/generate_trial.R")
source("../../code/functions/generate_dataset.R")
source("../../code/functions/sample_data.R")
source("../../code/functions/getStatistics.R")


# Functions to set up the model
################################
#source("../../code/functions/default_priors.R")
#source("../../code/functions/sample_parameters.R")


# JAGS related functions
###########################
source("../../code/functions/write_JAGSmodel.R")
source("../../code/functions/data_toJAGS.R")
source("../../code/functions/check_Rhat.R")
source("../../code/functions/default_inits.R")
source("../../code/functions/extractSamples.R")

# Manage results
################################################
source("../../code/functions/plot_Chain.R")
source("../../code/functions/plot_recovery.R")
source("../../code/functions/getDifferences_TRUEvsEST.R")
```

# Specify priors

```{r}
default_priors <- function(Show=TRUE, modelType=NA){
  prior <- data.frame("bound_mean_mean" = 2.25,  "bound_mean_sdev" = 1.00, # 99% density between {-0.07, 4.57}
                      "drift_mean_mean" = 0.00,  "drift_mean_sdev" = 3.00, # 99% density between {-6.9 , 6.9}
                      "nondt_mean_mean" = 0.55,  "nondt_mean_sdev" = 0.25, # 99% density between {-0.03, 1.13}
                      "bound_sdev_shape" = 3.00,  "bound_sdev_rate" = 0.50,   
                      "drift_sdev_shape" = 2.00,  "drift_sdev_rate" = 0.20,
                      "nondt_sdev_shape" = 4.00,  "nondt_sdev_rate" = 0.25)
  if(modelType!="hierarchical"){
            prior$betaweight_mean = 0
            prior$betaweight_sdev = 1
  }
  if(Show){       show_priors(prior)           }
  return(prior)
}
```

# Specify how to generate true parameters

```{r}
sample_parameters <- function(priors, nPart, modelType, X, criterion=NA, fromPrior=NA, Show=TRUE, fixedBeta = NA){
        # Hierarchical mean values are sampled from a uniform defined because...
        bound_mean <- runif(1,0.5,4)   # ...95% density of the default prior falls here
        drift_mean <- runif(1,-5,5)      # ...95% density of the default prior falls here
        nondt_mean <- runif(1,0.2,0.95) # ...95% density of the default prior falls here
        # Hierarchical standard deviations are sampled from arbitrary uniforms
        bound_sdev <- bound_mean/5
        drift_sdev <- abs(drift_mean/5)+0.01
        nondt_sdev <- nondt_mean/5
  bound <- rnorm(nPart,bound_mean, bound_sdev) # Extra-precaution / shouldn't be needed often
  drift <- rnorm(nPart,drift_mean, drift_sdev)
  nondt <- rnorm(nPart,nondt_mean, nondt_sdev) # Precaution
  parameter_set <- list("bound_mean" = bound_mean, "drift_mean" = drift_mean, "nondt_mean" = nondt_mean, 
                        "bound_sdev" = bound_sdev, "drift_sdev" = drift_sdev, "nondt_sdev" = nondt_sdev,
                        "bound" = bound,   "drift" = drift,   "nondt" = nondt)
  # Check modelType to determine the need for a coefficient
  if(!(modelType=="hierarchical"|is.na(modelType))){  
        if(!is.na(fixedBeta)){
          betaweight <- fixedBeta
          parameter_set$drift_sdev <- 0.25
          parameter_set$drift <- rnorm(nPart*2,drift_mean+betaweight*X, 0.25)
        }else{
            # Sample and add coefficient to the parameter_set
            if(criterion=="nondt"){   betaweight <- runif(1, 0, 1)
                             }else{   betaweight <- runif(1, -1, 1)       }
            # Identify criterion (i.e., parameter of interest)
            if(is.na(criterion)){  criterion <- "drift"  }
            if(criterion=="bound"){  parameter_set$bound <- rnorm(nPart,bound_mean+(betaweight*X), bound_sdev)  }
            if(criterion=="drift"){  parameter_set$drift <- rnorm(nPart,drift_mean+(betaweight*X), drift_sdev)  }
            if(criterion=="nondt"){  parameter_set$nondt <- rnorm(nPart,nondt_mean+(betaweight*X), nondt_sdev)  }
        }
    parameter_set <- c(parameter_set, list("betaweight" = betaweight))
  }
  
  if(Show){   show_parameters(parameter_set)    }
  return(parameter_set)
}
```

# Load core scripts

```{r, echo=FALSE}
source("../../code/scripts/HDDM_setup.R")
source("../../code/scripts/HDDM_runJAGS.R")
source("../../code/scripts/HDDM_runSims.R")
```

```{r file="../../code/scripts/HDDM_setup.R"}
```

```{r file="../../code/scripts/HDDM_runJAGS.R"}
```

```{r file= "../../code/scripts/HDDM_runSims.R"}
```

# Run simple simulation grid

```{r}
x <- HDDM_runSims(nParticipants = 20, nTrials = 20, nDatasets = 100,
                  modelType = "metaregression", criterion = "drift",
                  n.chains=4, forceSim = FALSE, fromPrior = FALSE)
```